---
title: "Pipeline"
author: "Camilla Eva Krænge"
date: "3/13/2023"
output:
  pdf_document: default
  html_document: default
---
This markdown was used to prepare the exp_1 tsv file with all the data used for further analyses and plotting. 

Overview:
- Load libraries and functions
- Load data
- Merge all tasks into one file 
- Fix GUI recording errors 
- Mark outlier response times and button press errors
- Save data file for analysis 

Load libraries and functions ##
```{r load libraries, include=FALSE, warning = FALSE}
# Ensure that pacman is installed
if (!require("pacman")) {
  install.packages("pacman")
  library("pacman")
}

### PLEASE REMOVE LIBRARIES THAT ARE NOT NEEDED TO RUN THIS RMARKDOWN

# Data Manipulation and Visualization
p_load(tidyverse, dplyr)

#Functions from GitHub
source(here::here("Analysis","functions","load_data.R")) 

source(here::here("Analysis","functions","clean_data.R")) 

```

#Experiment 1

## Load data ## 
Load  data for each task and save them into one data frame
```{r load data for each task, include=FALSE, warning = FALSE}
# Define BIDS directory 
WD = getwd() # WD should point to BIDS folder

#Load data for each task
fast_ss = load_data(WD, 'FastSS')
fast_li = load_data(WD, 'FastLI')
slow_ss = load_data(WD, 'SlowSS')
slow_li = load_data(WD, 'SlowLI')

# Create one df with all task files in one data frame 
df = rbind(fast_ss, fast_li, slow_ss, slow_li)

# Merge distance_size and area_size into one column
df$size <- coalesce(df$area_size, df$distance_size)

# Add a trial rep counter 
df <- df %>%
  group_by(ID, task, size, quality) %>%
  mutate(trial_rep = row_number()) %>% 
  ungroup() %>% 
  dplyr::rename(trial = ...1) 

```

Fix data recording GUI errors 
list of errors:
* ID 00 - FastSS marked as Pilot Y(N)
* ID 01 - FastLI marked as age 21(26) and Pilot Y(N), gender F(M)
* ID 04 - FastLI marked as Pilot Y(N) and FastSS age 21(28)
* ID 14 - SlowSS marked as Pilot Y(N)
* ID 15 - SlowSS marked as 25(27)

```{r}
df <- df %>% 
  # Fix pilot error
  mutate(pilot = ifelse(ID %in% c(0, 1, 4, 14), "N", pilot)) %>% 
  
  # Fix age errors
  mutate(age = ifelse(ID %in% 1, 26, age)) %>% 
  mutate(age = ifelse(ID %in% 4, 28, age)) %>% 
  mutate(age = ifelse(ID %in% 15, 27, age)) %>% 
  
  # Fix gender error
  mutate(gender = ifelse(ID %in% 1, 'M', gender)) %>% 
  
  # Fix F -> FALSE by chaning F to f and M to m, NB to nb 
  mutate(gender = case_when(
    gender == "M" ~ "m",
    gender == "FALSE" ~ "f",
    gender == "NB" ~ "nb",
    TRUE ~ as.character(gender))) 
```

Find outlier response times (corresponding to responses that were more than 3 SD larger than the average)
```{r Find outliers, include=FALSE, warning = FALSE}
df = find_outliers(df, 0)
```

Save experiment 1 data in a csv file
```{r}
write.csv(df, here::here("Data","exp1.csv"), row.names=FALSE)
```

